---
title: "Alcohol vs Seat choice"
author: "Your Name"
date: "Fall 2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r include=FALSE}
require(tidyverse)
require(tigerstats)
davisdata <- read.csv(file="UCDavis.csv")
```
## Our Goal is to answer this question Is there a difference between the alcohol consumed between the row you choose to sit in??

# introduction

$H_4$ There is no difference in the alcohol consumed based on the row sit in 

$H_A$ There is a difference in the alcohol consumed based on the row you sit in 

# Method

the response variable seat is a categorical variable, therefore we use numerical cat rmd. 

## Now with ggplot - first select the basic data

```{r}
basicCN <- ggplot(davisdata,aes(y=alcohol,x=Seat))
```
## Now add in boxplot

```{r}
basicCN + geom_boxplot()
```
  
  This box plot shows the amount of alcohol consumed by the seating position. The back seat consumes more than the front and the middle. The front and middle seats consume the same or slightly different. 
  
### get fancy  

```{r}
basicCN + geom_boxplot(notch=TRUE,outlier.color = "red") + stat_boxplot(geom ='errorbar') + labs(title="Fancy notch boxplot \n with 2 lines")
```

The graph shows the amount of alcohol consumed based on where you sit. The back seat people consume more alcohol than the people who sit in the front and middle. The middle consumes more than the people who sit in the front. 

## Numerical Summarys 

```{r}
favstats(alcohol~Seat,data=davisdata)
```

This data shows the mean and median of alcohol consumed. It also shows how they drink by each quarter. The people in the back drink way more than the people in the front and middle seats. 

## Inferential Tests

```{r}
model.1 <- aov(alcohol~Seat,data=davisdata)
summary.aov(model.1)
```

The p value is 0.000116 which is less than 0.05. The p value is smaller so therefore we reject the null hypothesis. This means that there is a difference in the alcohol consumption based on where they sit. 

```{r}
plot(TukeyHSD(model.1))
```


We don't have evidence that there is a difference in the alcohol consumption between the middle and front row. The only difference we found is the back row consumes more than the middle and front row. 

## Conclusions

Is there a difference between the alcohol consumed between the row you choose to sit in? Yes there is a difference between the alcohol consumed by the row you sit in. Based on the data the back row consumed more alcohol than the people who sit in the front and middle row. The p is 0.000116 which is smaller than 0.05 I will reject the null hypothesis. Therefore the back row people consume more alcohol. 
